Prag Bat

### 2020-02-21 analysis/data_processing.Rmd
fix timing ad hoc

```{r}
# importing data
### die flogenden Zeilen kannst du überspringen. Weiter gehts in Zeile 68
# files <- dir("~/Work/PragBat/raw_data/")
# 
# raw_data <- data_frame()
# for (f in files) {
#   jf <- paste("~/Work/PragBat/raw_data/",f,sep="")
#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
#   date <- str_sub(jf,33,str_length(jf)-11)
#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date, 
#                                                trial = as.character(trial))
#   raw_data <- bind_rows(raw_data, id)
# }
# 
# unique(raw_data$subid)
# 
# 
# task_data <- raw_data %>%
#   filter(trial != "training", 
#          trial != "filler1", 
#          trial != "filler2",
#          trial != "train",
#          trial != "train2")%>%
#   filter(phase == "shape" | is.na(phase))%>%
#   mutate(subid = recode(subid, `13.2` = "Vp13.2",
#                         `13.2` = "Vp13.2",
#                         `14.2` = "Vp14.2",
#                         `16.2` = "Vp16.2",
#                         `19.1` = "Vp19.1",
#                         `12.1` = "Vp12.1",
#                         `29.2` = "Vp29.2",
#                         `26.1` = "Vp26.2",
#                         `37.1` = "Vp37.1",
#                         `38.1` = "Vp38.1"
#                         ))%>%
#   select(subid, subage, test_date, task, trial, correct)%>%
#   separate(subid, into = c("id","test_day"), sep="\\.")%>%
#   mutate(test_day = ifelse(id == "Vp12" & test_date =="2019-11-26", 2, test_day))

#write_csv(task_data, "../data/data.csv")

@@

# log <- read_ods("../../VP Liste.ods", sheet = 2)%>%
#   mutate(age = as.numeric(difftime(test_day_1, `birthday `, units = "days"))/365.25,
#          id = paste("Vp",`ID `, sep = ""))%>%
#   select(id, age, status)
#   
# 
# data <- task_data %>%
#   left_join(log)%>%
#   mutate(check_age = ifelse(subage == substr(age,1,1),T,F))

data <- read_csv("../data/data.csv")%>%
  mutate(subage = factor(subage),
         trial = ifelse(test_day == "2", trial + 4, trial),
         z_age = age - mean(age))%>%
  select(-X)

@@

# card_sorting_model1 <- brm(correct ~ z_age + trial + (trial|id),
#                     data = card_sorting_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4, 
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/card_sorting_model1.rds")
# 
# card_sorting_model2 <- brm(correct ~ trial + (trial|id),
#                     data = card_sorting_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4, 
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/card_sorting_model2.rds")

>>>>

```{r}
#importing data
## die flogenden Zeilen kannst du überspringen. Weiter gehts in Zeile 68
files <- dir("~/Work/PragBat/raw_data/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/PragBat/raw_data/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,33,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date,
                                               trial = as.character(trial))
  raw_data <- bind_rows(raw_data, id)
}

unique(raw_data$subid)

task_data <- raw_data %>%
  filter(trial != "training",
         trial != "filler1",
         trial != "filler2",
         trial != "train",
         trial != "train2")%>%
  filter(phase == "shape" | is.na(phase))%>%
  mutate(subid = recode(subid, `13.2` = "Vp13.2",
                        `13.2` = "Vp13.2",
                        `14.2` = "Vp14.2",
                        `16.2` = "Vp16.2",
                        `19.1` = "Vp19.1",
                        `12.1` = "Vp12.1",
                        `29.2` = "Vp29.2",
                        `26.1` = "Vp26.2",
                        `37.1` = "Vp37.1",
                        `38.1` = "Vp38.1"
                        ),
         item = ifelse(task == "card_sorting", sample,leftObject))%>%
  select(subid, subage, test_date, task,item, trial, correct)%>%
  separate(subid, into = c("id","test_day"), sep="\\.")%>%
  mutate(test_day = ifelse(id == "Vp12" & test_date =="2019-11-26", 2, test_day))

@@

log <- read_ods("../../VP Liste.ods", sheet = 2)%>%
  mutate(age = as.numeric(difftime(test_day_1, `birthday `, units = "days"))/365.25,
         id = paste("Vp",`ID `, sep = ""))%>%
  select(id, age, status)

data <- task_data %>%
  left_join(log)%>%
  mutate(check_age = ifelse(subage == substr(age,1,1),T,F),
         subage = as.numeric(substr(age,1,1)),
         trial = as.numeric(trial))%>%
  select(-test_date, - status, -check_age)%>%
  mutate(trial = ifelse(test_day == "2", 
                        ifelse(task == "card_sorting", trial + 6, trial +5),
                        trial),
         z_age = age - mean(age),
         z_trial = trial - mean(trial))

write_csv(data, "../data/data.csv")

data <- read_csv("../data/data.csv")

@@

card_sorting_model1 <- brm(correct ~ z_age + trial + (trial|id),
                    data = card_sorting_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/card_sorting_model1.rds")

card_sorting_model2 <- brm(correct ~ trial + (trial|id),
                    data = card_sorting_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/card_sorting_model2.rds")
